Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2020-12-16 analysis/paper/paper.Rmd
Agrega números de línea

bibliography: 
  - AsymSAM
  - packages
bibstyle: spbasic
# bibstyle options spbasic(default), spphys, spmpsci
output: 
  bookdown::pdf_book: 
      base_format: rticles::springer_article
      latex_engine: "xelatex"
      citation_package: "natbib"
      # pandoc_args: ["--lua-filter=abstract-to-meta.lua"]
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
#  - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}
---

>>>>

bibliography: 
  - AsymSAM
  - packages
bibstyle: spbasic
# bibstyle options spbasic(default), spphys, spmpsci
output: 
  bookdown::pdf_book: 
      base_format: rticles::springer_article
      latex_engine: "xelatex"
      citation_package: "natbib"
      # pandoc_args: ["--lua-filter=abstract-to-meta.lua"]
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
#  - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}
 - \usepackage{lineno}
 - \linenumbers 
---
